Software Development Methodology

### 2024-02-14 latex/ms.tex
.

>>>>

On a higher level the directory should look like this:
\begin{verbatim}
$HOME/$PLATFORM_DOMAIN_NAME/$REPOSITORY_OWNER/$REPOSITORY_NAME/
\end{verbatim}

For example the directory structure that corresponds to the repository that hosts the source code of this paper is:
\begin{verbatim}
$HOME/github.com/pbizopoulos/a-makefile-for-developing-containerized-latex-technical-documents/
\end{verbatim}

In that way version control related commands could work between different machines. For example the following incorporates changes from all \texttt{github.com} remote repositories into the current branches using \texttt{git}:
\begin{verbatim}
find $HOME/github.com -name .git | xargs dirname | xargs -I{} -P0 git -C {} pull
\end{verbatim}
